Devito for large scale elastic modelling and anisotropic inversion

### 2020-04-20 paper.tex
Update tex file.

One of the main applications of seismic finite-difference modeling in
exploration geophysics is reverse-time migration (RTM), a wave-equation
based seismic imaging technique. Real-world seismic imaging presents a
number of challenges that make applying this method to industry-scale
problem sizes difficult. First of all, RTM requires an accurate
representation of the physics through sophisticated wave-equations such
as the tilted-transverse isotropic (TTI) wave-equation, for which both
forward and adjoint implementations have to be provided. Secondly,
wave-equations must be solved for a large number of independent
experiments, where each individual PDE solve in itself is expensive in
terms of FLOPs and memory usage. For certain workloads, limited domain
decomposition, that balances the domain size and the number of
independent experiments, and checkpointing techniques have to be applied.
In the following sections, we describe an industry-scale seismic imaging
problem presenting all of the aforementioned challenges, its
implementation with Devito, and the results of an experimentation
carried out on the Azure Cloud using a synthetic data set.

@@

In our seismic imaging case study, we use an anisotropic representation
of the physics called Tilted Transverse Isotropic (TTI) modeling
\cite{thomsen1986}. This representation for wave motion is one of the
most widely used in exploration geophysics since it captures the leading
order kinematics and dynamics of acoustic wave motion in highly
heterogeneous elastic media where the medium properties vary more
rapidly in the direction perpendicular to sedimentary strata
\cite{alkhalifah2000, baysal1983, bubetti2012, bubetti2014, bubesatti2016, chu2011, duveneck, fletcher, fowlertti2010, louboutin2018segeow, whitmore1983, witte2016segpve, xu2014, zhang2005, zhang2011, zhan2013}.
The TTI wave-equation is an acoustic, low dimensional (4 parameters, 2
wavefields) simplification of the 21 parameters and 12 wavefields
tensorial equations of motions \cite{hooke}. This simplified
representation is parametrized by the Thomsen parameters
$\epsilon(x), \delta(x)$ that relate to the global (many wavelength
propagation) difference in propagation speed in the vertical and
horizontal directions, and the tilt and azimuth angles
$\theta(x), \phi(x)$ that define the rotation of the vertical and
horizontal axis around the cartesian directions. However, unlike the
scalar isotropic acoustic wave-equation itself, the TTI wave-equation is
extremely computationally costly to solve and it is also not
self-adjoint as shown in \cite{louboutin2018segeow}.

The main complexity of the TTI wave-equation is due to rotation of the
symmetry axis of the physics that leads to rotated second-order
finite-difference stencils. In order to ensure numerical stability,
these rotated finite-difference operators are designed to be
self-adjoint (c.f. \cite{zhang2011, duveneck}). For example, we define
the rotated second order derivative with respect to $x$ as:
%
\begin{equation}
\begin{aligned}
  G_{\bar{x}\bar{x}} &= D_{\bar{x}}^T D_{\bar{x}} \\
  D_{\bar{x}} &= \cos(\mathbf{\theta})\cos(\mathbf{\phi})\frac{\mathrm{d}}{\mathrm{d}x} + \cos(\mathbf{\theta})\sin(\mathbf{\phi})\frac{\mathrm{d}}{\mathrm{d}y} - \sin(\mathbf{\theta})\frac{\mathrm{d}}{\mathrm{d}z}.
\end{aligned}
\label{rot}
\end{equation}
%
 We enable the simple expression of these complex stencils in
\href{https://github.com/devitocodes/devito}{Devito} as
finite-difference shortcuts, such as \texttt{u.dx} where \texttt{u} is a
\texttt{Function}, are enabled not only for the basic types but for
generic expressions, for example
\texttt{(u\phantom{\ }+\phantom{\ }v.dx).dy}. As a consequence, the
rotated derivative defined in~\ref{rot} is implemented with
\href{https://github.com/devitocodes/devito}{Devito} in two lines as:

@@

Note that while the adjoint of the finite-difference stencil is enabled
via the standard Python \texttt{.T} shortcut, the expression needs to be
reordered by hand as the tilt and azymuth angle are spatially dependent
and require to be inside the second pass of first-order derivative. We
can see from these simple two lines that the rotated stencil involves
all second-order derivatives (\texttt{.dx.dx}, \texttt{.dy.dy} and
\texttt{.dz.dz}) and all second-order cross-derivatives (\texttt{dx.dy},
\texttt{.dx.dz} and \texttt{.dy.dz}) that leads to a denser stencil
support and higher computational complexity (c.f.
\cite{louboutin2016ppf}). For illustration purpose, the complete
generated code for tti modeling with and without MPI is made available
at
\href{https://github.com/mloubout/SC20Paper/tree/master/gencode}{CodeSample}
in \texttt{tti-so8.c} and \texttt{tti-so8-mpi.c}.

Because of the very high number of floating-point operations (FLOP)
needed per grid point for the weighted rotated Laplacian, this
anisotropic wave-equation is extremely challenging to implement. As we
show in Table~\ref{ttiFLOPs}, and previously analysed in
\cite{louboutin2016ppf}, the computational cost with high-order
finite-difference is in the order of thousands of FLOPs per grid point
without optimizations.

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule\addlinespace
spatial order & w/o optimizations & w/ optimizations\tabularnewline
\midrule
4 & 501 & 95\tabularnewline
8 & 539 & 102\tabularnewline
12 & 1613 & 160\tabularnewline
16 & 5489 & 276\tabularnewline
\bottomrule
\end{tabular}
\caption{Per-grid-point FLOPs of the finite-difference stencil for the
TTI wave-equation with different spatial discretization
orders.}\label{ttiFLOPs}
\end{table}

The version without FLOP-reducing optimizations is a direct translation
of the discretized operators into stencil expressions. The version with
optimizations employs transformations such as common sub-expressions
elimination, factorization, and cross-iteration redundancy elimination
-- the latter being key in removing the redundancies induced by mixed
derivatives. Implementing all of these techniques manually is inherently
difficult and laborious. Further, to obtain the desired performance
improvements it is necessary to orchestrate them with aggressive loop
fusion (for data locality), tiling (for data locality and tensor
temporaries), and potentially ad-hoc vectorization strategies (if
rotating registers are used). While an explanation of the optimization
strategy employed by
\href{https://github.com/devitocodes/devito}{Devito} is beyond the scope
of this paper (see \cite{devito-compiler} for details), what should be
appreciated here is that all this complexity is hidden away from the
users.

With such complex physics, mathematics, and engineering, it becomes
evident that the implementation of a solver for this wave-equation is
exceptionally time-consuming and can lead to thousands of lines of code
even for a single type of discretization. The verification of the result
is no less complicated, since any small error is effectively untrackable
and any change to the finite-difference scheme or to the time-stepper is
difficult to achieve without substantial re-coding. Another complication
stems from the fact that practitioners of seismic inversion are often
geoscientists and not computer scientists/programmers. Unfortunately,
this background often either results in poorly written low performant
codes or it leads to complications when research codes are handed off to
computer scientists who know how to write fast codes but who often miss
the necessary geophysical domain knowledge. Neither situation is
conducive to addressing the complexities that come with implementing
codes based on the latest geophysical insights and high-performance
computing. With \href{https://github.com/devitocodes/devito}{Devito} on
the other hand, both the forward and adjoint equations can be
implemented in a few lines of Python code as illustrated with the
rotational operator in \#rotxpy.

Simulation of wave motion is only one aspect of solving problems in
seismology. During wave-equation based imaging, we also need to compute
sensitivities (gradient) with respect to the quantities of interest.
This imposes additional constraints on the design and implementations of
our simulation codes as outlined in \cite{virieux}. Among several
factors, such as fast setup time, we focused on correct and testable
implementations for the adjoint wave-equation and the gradient (action
of the adjoint Jacobian)
\cite{louboutin2018segeow, louboutin2020THmfi}, which exactness is
mandatory requirements for gradient based iterative optimization
algorithms.

@@

We now demonstrate the scalability of
\href{https://github.com/devitocodes/devito}{Devito} to real-world
applications with the imaging of an industry-scale three-dimensional TTI
subsurface model. This imaging was carried out in the Cloud on Azure and
takes advantage of recent work to port conventional cluster code to the
Cloud using a serverless approach. The serverless implementation is
described in detail in \cite{witte2019TPDedas, witte2019SEGedw} and
describes the steps to run computationnaly and financially efficient HPC
workloads in the Cloud. This imaging project, in collaboration with
Azure, demonstrates the scalability and robustness of
\href{https://github.com/devitocodes/devito}{Devito} to large scale
wave-equation based inverse problems and its cost-effectiveness in
combination with a serverless implementation of seismic imaging in the
Cloud. In this example, we imaged a synthetic three-dimensional
anisotropic subsurface model that mimics a realistic industry size
problem with a realistic representation of the physics (TTI). The
physical size of the problem is \texttt{10kmx10kmx2.8km} discretized on
a \texttt{12.5m} grid with 40 points of absorbing layer on each sides
that leads to \texttt{881x881x371} computational grid points (300
Million grid points). The final image is the sum of 1500 single-source
images and we computed 100 single-source images in parallel on 200 nodes
available using two nodes per source experiment.

@@

We briefly describe the computational setup and the performance achieved
for this anisotropic imaging problem. Due to time constraints, and
because the resources we were given access to for this proof of concept
with Azure were somewhat limited, we did not have access to HPC virtual
machines (VM) nor Infiniband enabled ones. The nodes we ran this
experiment on are \texttt{Standard\_E64\_v3} and
\texttt{Standard\_E64s\_v3} that while not HPC VM are memory optimized
allowing to save the wavefield in memory for imaging (TTI adjoint state
gradient \cite{virieux, louboutin2018segeow}). These VMs are Intel®
Broadwell E5-2673 v4 2.3GH that are dual socket, 32 physical cores (and
hyperthreading enabled) and 432Gb of DRAM. The overall inversion
involved computing the image for 1500 source positions, i.e.~solving
1500 forward and 1500 adjoint TTI wave-equations. A single image
required 600Gb of memory in single precision and we used two VMs per
source with MPI with one rank per socket (4 MPI ranks per source) and
imaged 100 sources in parallel. The performance achieved, in single
precision, was as follow:

@@

We also observe that if we had had access to more resources, and because
the imaging problem is embarassingly parallel over sources and can scale
to any computational resources, we could have attempted imaging of all
of the 1500 sources in parallel, which theoretically leads to a
performance of 0.4PFLOP/s.

\textbf{\emph{How was the performance measured}}

The execution time is computed through Python-level timers prefixed by
an MPI barrier. The floating-point operations are counted once all of
the symbolic FLOP-reducing transformations have been performed during
compilation. \href{https://github.com/devitocodes/devito}{Devito} uses
an in-house estimate of cost, rather than \texttt{SymPy}'s estimate, to
take care of some low-level intricacies. For example, Devito's estimate
ignores the cost of integer arithmetic used for offset indexing into
multi-dimensional arrays. To calculate the total number of FLOPs
performed, \href{https://github.com/devitocodes/devito}{Devito}
multiplies the floating-point operations calculated at compile time by
the size of the iteration space, and it does that at the granularity of
individual expressions. Thanks to aggressive code motion, the amount of
innermost-loop-invariant sub-expressions in a
\href{https://github.com/devitocodes/devito}{Devito} Operator is
typically negligible, so the
\href{https://github.com/devitocodes/devito}{Devito} estimate does not
basically suffer from this issue, or at least not in a tangible way to
the best of our knowledge. The Devito-reported GFLOP/s were also checked
against those produced by Intel Advisor on several single-node
experiments: the differences -- typically
\href{https://github.com/devitocodes/devito}{Devito} underestimating the
achieved performance -- were always at most in the order of units, and
therefore negligible.

@@

The subsurface velocity model that was used in this study is an
artificial anisotropic model that is designed and built combining two
broadly known and used open-source SEG/EAGE acoustic velocity models
that come each with realistic geophysical imaging challenges such as
sub-salt imaging. The anisotropy parameters are derived from a smoothed
version of the velocity while the tilt angles were derived from a
combination of the smooth velocity models and vertical and horizontal
edge detection. The final seismic image of the subsurface model is
plotted in Figure~\ref{OverTTI} and highlights the fact that 3D seismic
imaging based on a serverless approach and automatic code generation is
feasible and provides good results on a realistic model.

@@

\cite{witte2019TPDedas} fully describes the serverless implementation
of seismic inverse problems, including iterative algorithms for
least-square minimization problems (LSRTM). The 3D anisotropic imaging
results were presented as part of a keynote presentation at the EAGE HPC
workshop in October 2019 \cite{herrmann2019EAGEHPCaii} and at the Rice
O\&G HPC workshop \cite{witte2019RHPCssi} where we focused on the
serverless implementation of seismic inversion algorithms in the Cloud.
This work illustrates the flexibility and portability of Devito, as we
were able to easily port a code only tested and developed on local
hardware to the Cloud, with only minor adjustments. This portability
included the possibility to run MPI-based code for domain decomposition
in the Cloud, after developing it on a desktop computer. Our experiments
are reproducible using the instructions in a public repository
\href{https://github.com/slimgroup/Azure2019}{AzureTTI}, which contains,
among the other things, the Dockerfiles and Azure
\href{https://batch-shipyard.readthedocs.io}{batch-shipyard} setup. This
example can also easily ber un on a traditional HPC cluster environment
using for example \href{https://github.com/slimgroup/JUDI.jl}{JUDI} or
Dask \cite{dask} for parallelization over sources.

>>>>

One of the main applications of seismic finite-difference modeling in
exploration geophysics is reverse-time migration (RTM), a wave-equation based
seismic imaging technique. Real-world seismic imaging presents a number of
challenges that make applying this method to industry-scale problem sizes
difficult. Firstly, RTM requires an accurate representation of the underlying
physics via sophisticated wave-equations such as the tilted-transverse isotropic
(TTI) wave-equation, for which both forward and adjoint implementations must to
be provided. Secondly, wave-equations must be solved for a large number of
independent experiments, where each individual PDE solve is itself expensive in
terms of FLOPs and memory usage. For certain workloads, limited domain
decomposition, that balances the domain size and the number of independent
experiments, and checkpointing techniques must to be adopted. In the following
sections, we describe an industry-scale seismic imaging problem that poses all
the aforementioned challenges, its implementation with Devito, and the results
of an experiment carried out on the Azure Cloud using a synthetic data set.

@@

In our seismic imaging case study, we use an anisotropic representation of the
physics called Tilted Transverse Isotropic (TTI) modeling \cite{thomsen1986}. This
representation for wave motion is one of the most widely used in exploration
geophysics since it captures the leading order kinematics and dynamics of
acoustic wave motion in highly heterogeneous elastic media where the medium
properties vary more rapidly in the direction perpendicular to sedimentary
strata \cite{alkhalifah2000, baysal1983, bubetti2012, bubetti2014,
bubesatti2016, chu2011, duveneck, fletcher, fowlertti2010,
louboutin2018segeow, whitmore1983, witte2016segpve, xu2014, ,zhang2005,
zhang2011, zhan2013}. The TTI wave-equation is an acoustic, low dimensional (4
parameters, 2 wavefields) simplification of the 21 parameter and 12 wavefields
tensorial equations of motions \cite{hooke}. This simplified representation is
parametrized by the Thomsen parameters $\epsilon(x), \delta(x)$ that relate to
the global (propagation over many wavelengths) difference in propagation speed
in the vertical and horizontal directions, and the tilt and azimuth angles
$\theta(x), \phi(x)$ that define the rotation of the vertical and horizontal
axis around the cartesian directions. However, unlike the scalar isotropic
acoustic wave-equation itself, the TTI wave-equation is extremely
computationally costly to solve and it is also not self-adjoint as shown in
\cite{louboutin2018segeow}.

The main complexity of the TTI wave-equation is that the rotation of the
symmetry axis of the physics leads to rotated second-order finite-difference
stencils. In order to ensure numerical stability, these rotated
finite-difference operators are designed to be self-adjoint (c.f.
\cite{zhang2011, duveneck}). For example, we define the rotated second order
derivative with respect to $x$ as:
%
\begin{equation}
\begin{aligned}
  G_{\bar{x}\bar{x}} &= D_{\bar{x}}^T D_{\bar{x}} \\
  D_{\bar{x}} &= \cos(\mathbf{\theta})\cos(\mathbf{\phi})\frac{\mathrm{d}}{\mathrm{d}x} + \cos(\mathbf{\theta})\sin(\mathbf{\phi})\frac{\mathrm{d}}{\mathrm{d}y} - \sin(\mathbf{\theta})\frac{\mathrm{d}}{\mathrm{d}z}.
\end{aligned}
\label{rot}
\end{equation}
%
 We enable the simple expression of these complicated stencils in
\href{https://github.com/devitocodes/devito}{Devito} as
finite-difference shortcuts such as \texttt{u.dx} where \texttt{u}
is a \texttt{Function}. Such shortcuts are enabled not only for the
basic types but for generic composite expressions, for example
\texttt{(u\phantom{\ }+\phantom{\ }v.dx).dy}. As a consequence, the
rotated derivative defined in~\ref{rot} is implemented with
\href{https://github.com/devitocodes/devito}{Devito} in two lines as:

@@

Note that while the adjoint of the finite-difference stencil is enabled via the
standard Python \texttt{.T} shortcut, the expression needs to be reordered by hand
since the tilt and azymuth angles are spatially dependent and require to be
inside the second pass of first-order derivative. We can see from these simple
two lines that the rotated stencil involves all second-order derivatives
(\texttt{.dx.dx}, \texttt{.dy.dy} and \texttt{.dz.dz}) and all second-order
cross-derivatives (\texttt{dx.dy}, \texttt{.dx.dz} and \texttt{.dy.dz}) which
leads to a denser stencil support and higher computational complexity
(c.f. \cite{louboutin2016ppf}). For illustrative purposes, the complete
generated code for tti modeling with and without MPI is made available
at \href{https://github.com/mloubout/SC20Paper/tree/master/gencode}{CodeSample}
in \texttt{tti-so8.c} and \texttt{tti-so8-mpi.c}.

Owing to the very high number of floating-point operations (FLOPs) needed per
grid point for the weighted rotated Laplacian, this anisotropic wave-equation is
extremely challenging to implement. As we show in Table Table~\ref{ttiFLOPs},
and previously analysed in \cite{louboutin2016ppf}, the computational cost with
high-order finite-difference is in the order of thousands of FLOPs per grid
point without optimizations. The version without FLOP-reducing optimizations is
a direct translation of the discretized operators into stencil expressions. The
version with optimizations employs transformations such as common
sub-expressions elimination, factorization, and cross-iteration redundancy
elimination -- the latter being key in removing redundancies introduced by mixed
derivatives. Implementing all of these techniques manually is inherently
difficult and laborious. Further, to obtain the desired performance improvements
it is necessary to orchestrate them with aggressive loop fusion (for data
locality), tiling (for data locality and tensor temporaries), and potentially
ad-hoc vectorization strategies (if rotating registers are used). While an
explanation of the optimization strategies employed by
\href{https://github.com/devitocodes/devito}{Devito} is beyond the scope of this
paper (see \cite{devito-compiler} for details), what is emphasized here is that
users can easily take full advantage of these optimization without needed to
concern themselves with the details.

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule\addlinespace
spatial order & w/o optimizations & w/ optimizations\tabularnewline
\midrule
4 & 501 & 95\tabularnewline
8 & 539 & 102\tabularnewline
12 & 1613 & 160\tabularnewline
16 & 5489 & 276\tabularnewline
\bottomrule
\end{tabular}
\caption{Per-grid-point FLOPs of the finite-difference TTI wave-equation stencil
with different spatial discretization orders.}\label{ttiFLOPs}
\end{table}

It is evident that developing an appropriate solver for the TTI wave-equation,
an endeavor involving complicated physics, mathematics, and engineering, is
exceptionally time-consuming and can lead to thousands of lines of code even for
a single choice of discretization. Verification of the results is no less
complicated, any minor error is effectively untrackable and any change to the
finite-difference scheme or to the time-stepping algorithm is difficult to
achieve without substantial re-coding. Another complication stems from the fact
that practitioners of seismic inversion are often geoscientists, not computer
scientists/programmers. Low level implementations from non-specialists can often
often lead to poorly performing code. However, if research codes are passed to
specialists in the domain of low level code optimization they often lack the
necessary geophysical domain knowledge, resulting in code that may lack a key
feature required by the geoscientist. Neither situation is conducive to
addressing the complexities that come with implementing codes based on the
latest geophysical insights in tandem with those from high-performance
computing. With \href{https://github.com/devitocodes/devito}{Devito} on the
other hand, both the forward and adjoint equations can be implemented in a few
lines of Python code as illustrated with the rotated operator in \#rotxpy. The
low level optimization element of the development is then taken care of under
the hood by the \href{https://github.com/devitocodes/devito}{Devito} compiler.

The simulation of wave motion is only one aspect of solving problems in
seismology. During wave-equation based imaging, it is also required to compute
sensitivities (gradient) with respect to the quantities of interest. This
requirement imposes additional constraints on the design and implementation of
model codes as outlined in \cite{virieux}. Along with several factors, such as
fast setup time, we focused on correct and testable implementations for the
adjoint wave-equation and the gradient (action of the adjoint Jacobian)
\cite{louboutin2018segeow, louboutin2020THmfi}; exactness being a mandatory
requirement of gradient based iterative optimization algorithms.

@@

We now demonstrate the scalability of
\href{https://github.com/devitocodes/devito}{Devito} to real-world applications
by imaging an industry-scale three-dimensional TTI subsurface model. This
imaging was carried out in the Cloud on Azure and takes advantage of recent work
to port conventional cluster code to the Cloud using a serverless approach. The
serverless implementation is detailed in \cite{witte2019TPDedas,
witte2019SEGedw} where the steps to run computationally and financially
efficient HPC workloads in the Cloud are described. This imaging project, in
collaboration with Azure, demonstrates the scalability and robustness of
\href{https://github.com/devitocodes/devito}{Devito} to large scale
wave-equation based inverse problems in combination with a cost-effective
serverless implementation of seismic imaging in the Cloud. In this example, we
imaged a synthetic three-dimensional anisotropic subsurface model that mimics a
realistic industry size problem with a realistic representation of the physics
(TTI). The physical size of the problem is \texttt{10kmx10kmx2.8km} discretized
on a \texttt{12.5m} grid with absorbing layers of width 40 grid points on each
side leading to \texttt{881x881x371} computational grid points ($\approx300$
Million grid points). The final image is the sum of 1500 single-source images:
100 single-source images were computed in parallel on the 200 nodes available
using two nodes per source experiment.

@@

We briefly describe the computational setup and the performance achieved for
this anisotropic imaging problem. Due to time constraints, and because the
resources we were given access to for this proof of concept with Azure were
somewhat limited, we did not have access to HPC virtual machines (VM) nor
Infiniband enabled ones. This experiment was carried out on
\texttt{Standard\_E64\_v3} and \texttt{Standard\_E64s\_v3} nodes which, while
not HPC VM nodes, are memory optimized thus allowing to the wavefield to be
stored in memory for imaging (TTI adjoint state gradient \cite{virieux,
louboutin2018segeow}). These VMs are Intel® Broadwell E5-2673 v4 2.3GH that are
dual socket, 32 physical cores (with hyperthreading enabled) and 432Gb of DRAM.
The overall inversion involved computing the image for 1500 source positions,
i.e.~solving 1500 forward and 1500 adjoint TTI wave-equations. A single image
required, in single precision, 600Gb of memory. Two VMs were used per source and
MPI set with one rank per socket (4 MPI ranks per source) and 100 sources were
imaged in parallel. The performance achieved was as follows:

@@

We comment that if more resources were available, and because the imaging
problem is embarrassingly parallel over sources and can scale arbitrarily,the
imaging of all of the 1500 sources in parallel could have been attempted, which
theoretically leads to a performance of 0.4PFLOP/s.

\textbf{\emph{How performance was measured}}

The execution time is computed through Python-level timers prefixed by an MPI
barrier. The floating-point operations are counted once all of the symbolic
FLOP-reducing transformations have been performed during compilation.
\href{https://github.com/devitocodes/devito}{Devito} uses an in-house estimate
of cost, rather than \texttt{SymPy}'s estimate, to take care of some low-level
intricacies. For example, Devito's estimate ignores the cost of integer
arithmetic used for offset indexing into multi-dimensional arrays. To calculate
the total number of FLOPs performed,
\href{https://github.com/devitocodes/devito}{Devito} multiplies the
floating-point operations calculated at compile time by the size of the
iteration space, and it does that at the granularity of individual expressions.
Thanks to aggressive code motion, the amount of innermost-loop-invariant
sub-expressions in a \href{https://github.com/devitocodes/devito}{Devito}
Operator is typically negligible and therefore the
\href{https://github.com/devitocodes/devito}{Devito} estimate does not suffer
from this issue, or at least not, to the best of our knowledge, in a tangible
way. The Devito-reported GFLOP/s were also checked against those produced by
Intel Advisor on several single-node experiments: the differences -- typically
\href{https://github.com/devitocodes/devito}{Devito} underestimating the
achieved performance -- were always at most in the order of units, and therefore
negligible.

@@

The subsurface velocity model used in this study is an artificial anisotropic
model that is designed and built combining two broadly known and used
open-source SEG/EAGE acoustic velocity models that each come with realistic
geophysical imaging challenges such as sub-salt imaging. The anisotropy
parameters are derived from a smoothed version of the velocity while the tilt
angles were derived from a combination of the smooth velocity models and
vertical and horizontal edge detection. The final seismic image of the
subsurface model is displayed in Figure~\ref{OverTTI} and highlights the fact
that 3D seismic imaging based on a serverless approach and automatic code
generation is feasible and provides good results.

@@

\cite{witte2019TPDedas} describe the serverless implementation of seismic
inverse problems in detail, including iterative algorithms for least-square
minimization problems (LSRTM). The 3D anisotropic imaging results were presented
as part of a keynote presentation at the EAGE HPC workshop in October 2019
\cite{herrmann2019EAGEHPCaii} and at the Rice O\&G HPC workshop
\cite{witte2019RHPCssi} in which the focus was on the serverless implementation
of seismic inversion algorithms in the Cloud. This work illustrates the
flexibility and portability of Devito: we were able to easily port a code
developed and tested on local hardware to the Cloud, with only minor
adjustments. Further, note that this experiment included the porting of
MPI-based code for domain decomposition developed on desktop computers to the
Cloud. Our experiments are reproducible using the instructions in a public
repository \href{https://github.com/slimgroup/Azure2019}{AzureTTI}, which
contains, among the other things, the Dockerfiles and Azure
\href{https://batch-shipyard.readthedocs.io}{batch-shipyard} setup. This example
can also be easily run on a traditional HPC cluster environment using, for
example, \href{https://github.com/slimgroup/JUDI.jl}{JUDI} or Dask~\cite{dask}
for parallelization over sources.
